---
title: "Profiling Report: bfmSpatial"
output: html_document
---

This report discusses the main results of profiling the bfmSpatial function according to the [tutorial](http://www.loicdutrieux.com/bfastSpatial/).  



## Experiment Details

The script to rerun analyses is shown below. 

```{r, eval=F}



library(bfastSpatial)
data(tura)

tura.subset = crop(tura, extent(tura, 1, 40, 1, 40))

Rprof(NULL)
Rprof(filename="tura.subset_prof_stack_3.out",interval=0.01,line.profiling = F)
bfmSpatial(tura.subset, start=c(2009, 1),type="OLS-MOSUM", history = "all") 
Rprof(NULL)
res = summaryRprof("tura.subset_prof_stack_3.out")
res$by.total
```




## Results


The table below show the R profiler output.
```{r}
res = summaryRprof("tura.subset_prof_stack_3.out")
res$by.total
``` 






Below, you can find additional conclusions how optimization of particular bfast functions would affect overall computation times of `bfmSpatial()`
```{r, echo=F}
res = summaryRprof("tura.subset_prof_stack_3.out")

speedup = 2
c = 1/speedup

totalspeedup <- function(fname, s=speedup) {
  c = 1/s
  lambda = res$by.total[paste("\"",fname,"\"",sep=""),]$total.time / res$by.total["\"bfmSpatial\"",]$total.time
  return(round(1/(1-lambda*(1-c)),digits = 2))
  #return(1/(1-(c*res$by.total[paste("\"",fname,"\"",sep=""),]$total.pct/100)))
}

functionspeedup <- function(fname, S=2) {
  lambda = res$by.total[paste("\"",fname,"\"",sep=""),]$total.time / res$by.total["\"bfmSpatial\"",]$total.time
  res = lambda/ ( (1/S) - 1 + lambda )
  if (is.na(res)) return (NA)
  if (res < 0) return(NA)
  return(round(res,digits=2))
  #return(round(1/(1+(-1 + 1/S)/(lambda)),digits=2))
}

#totalspeedup.bfastts = 1/(1-(c*res$by.total["\"bfastts\"",]$total.pct/100))
#totalspeedup.bfastmonitor= 1/(1-(c*res$by.total["\"bfastmonitor\"",]$total.pct/100))
```

* Speeding up `bfastmonitor()` by a factor of `r speedup` would have sped up `bfmSpatial()` by a factor of `r totalspeedup("bfastmonitor")`
* Speeding up `bfastts()` by a factor of `r speedup` would have sped up `bfmSpatial()` by a factor of `r totalspeedup("bfastts")`
* Speeding up `bfastpp()` by a factor of `r speedup` would have sped up `bfmSpatial()` by a factor of `r totalspeedup("bfastpp")`
* Speeding up `efp()` by a factor of `r 10` would have sped up `bfmSpatial()` by a factor of `r totalspeedup("efp",10)`
* Speeding up `recresid()` by a factor of `r 10` would have sped up `bfmSpatial()` by a factor of `r totalspeedup("recresid",10)`

To speed up `bfmSpatial()` by a factor of 2, you could do either

* speed up `bfastmonitor()` by a factor of `r functionspeedup("bfastmonitor",2)`,
* speed up `bfastts()` by a factor of `r functionspeedup("bfastts",2)`,
* speed up `bfastpp()` by a factor of `r functionspeedup("bfastpp",2)`,
* speed up `efp()` by a factor of `r functionspeedup("efp",2)`, or
* speed up `recresid()` by a factor of `r functionspeedup("recresid",2)`.






## Notes
Given computation times highly depend on the used hardware. In all experiments, a desktop workstation running Ubuntu 14.04 with an Intel Xeon 2.67GHz quad core CPU and 6 GB main memory has been used. Further system information can be found below. To simplify profiling multicore support of R operations was turned off. 


```{r}
suppressPackageStartupMessages(library(bfastSpatial,quietly=T))
sessionInfo()
``` 