---
title: "Profiling Report: bfast"
output: html_document
---
  
This report discusses the main results of profiling the bfast function using randomly generated timeseries.



## Experiment Details

The script to rerun analyses is shown below. 

```{r, eval=F}
library(bfast)
freq = 24
n = 1000

# simple linear trend
breakidx = n*0.6
trend1 = rep(0.6,breakidx)
trend2 = rep(0.4,n-breakidx)
trend = c(trend1,trend2)
seasonal = 0.05*sin(2*pi*(1:n)/freq)
noise = rnorm(n,0,0.05)
evi.random <- trend + seasonal + noise
series = ts(evi.random,start = c(1900,1), frequency = freq)
#plot(series)


Rprof(NULL)
Rprof(filename="random_bfast_1.out",interval=0.01,line.profiling = F)
bfast(series,season="harmonic", max.iter=1,breaks=1)
Rprof(NULL)
res = summaryRprof("random_bfast_1.out")
res$by.total
```




## Results


The table below show the R profiler output.
```{r}
res = summaryRprof("random_bfast_1.out")
res$by.total
``` 




Below, you can find additional conclusions how optimization of particular functions would affect overall computation times of `bfast()`
```{r, echo=F}
res = summaryRprof("random_bfast_1.out")

speedup = 2
c = 1/speedup

totalspeedup <- function(fname, s=speedup) {
  c = 1/s
  lambda = res$by.total[paste("\"",fname,"\"",sep=""),]$total.time / res$by.total["\"bfast\"",]$total.time
  return(round(1/(1-lambda*(1-c)),digits = 2))
  #return(1/(1-(c*res$by.total[paste("\"",fname,"\"",sep=""),]$total.pct/100)))
}

functionspeedup <- function(fname, S=2) {
  lambda = res$by.total[paste("\"",fname,"\"",sep=""),]$total.time / res$by.total["\"bfast\"",]$total.time
  res = lambda/ ( (1/S) - 1 + lambda )
  if (res < 0) return(NA)
  return(round(res,digits=2))
  #return(round(1/(1+(-1 + 1/S)/(lambda)),digits=2))
}

#totalspeedup.bfastts = 1/(1-(c*res$by.total["\"bfastts\"",]$total.pct/100))
#totalspeedup.bfastmonitor= 1/(1-(c*res$by.total["\"bfastmonitor\"",]$total.pct/100))

```

* Speeding up `recresid()` by a factor of `r 2` would have sped up `bfast()` by a factor of `r totalspeedup("recresid",2)`
* Speeding up `recresid()` by a factor of `r 10` would have sped up `bfast()` by a factor of `r totalspeedup("recresid",10)`


## Notes
Given computation times highly depend on the used hardware. In all experiments, a desktop workstation running Ubuntu 14.04 with an Intel Xeon 2.67GHz quad core CPU and 6 GB main memory has been used. Further system information can be found below. To simplify profiling multicore support of R operations was turned off. 


```{r}
suppressPackageStartupMessages(library(bfastSpatial,quietly=T))
sessionInfo()
``` 