---
title: "Profiling Report: bfastmonitor"
output: html_document
---

This report discusses the main results of profiling the bfastmonitor function using the (repeated) som timeseries from the `bfast` package.



## Experiment Details

The script to rerun analyses is shown below. 

```{r, eval=T,message=FALSE,warning=F,error=F}
library(bfast)
library(zoo)
k = 100
som2 = data.frame(Time = c(som$Time,max(som$Time)+  (1:(length(som$Time)*(k-1)))*0.04347826),
                  NDVI.a = rep(som$NDVI.a,k),
                  NDVI.b = rep(som$NDVI.b,k))
                  
NDVIa <- as.ts(zoo(som2$NDVI.a, som2$Time))
#plot(NDVIa)

## apply the bfast monitor function on the data
## start of the monitoring period is c(2434, 13)
## and the ROC method is used as a method to automatically identify a stable history
Rprof(NULL)
Rprof(filename="som_bfastmonitor_1.out",interval=0.005,line.profiling = F)
mona <- bfastmonitor(NDVIa, start = c(2434, 13), history = "all", type ="OLS-MOSUM")
Rprof(NULL)
res = summaryRprof("som_bfastmonitor_1.out")
#res$by.total
#plot(mona)
```




## Results

The table below show the R profiler output.
```{r}
res = summaryRprof("som_bfastmonitor_1.out")
res$by.total
``` 




Below, you can find additional conclusions how optimization of particular functions would affect overall computation times of `bfast()`
```{r, echo=F}
res = summaryRprof("som_bfastmonitor_1.out")

speedup = 2
c = 1/speedup

totalspeedup <- function(fname, s=speedup) {
  c = 1/s
  lambda = res$by.total[paste("\"",fname,"\"",sep=""),]$total.time / res$by.total["\"bfastmonitor\"",]$total.time
  return(round(1/(1-lambda*(1-c)),digits = 2))
  #return(1/(1-(c*res$by.total[paste("\"",fname,"\"",sep=""),]$total.pct/100)))
}

functionspeedup <- function(fname, S=2) {
  lambda = res$by.total[paste("\"",fname,"\"",sep=""),]$total.time / res$by.total["\"bfastmonitor\"",]$total.time
  res = lambda/ ( (1/S) - 1 + lambda )
  if (res < 0) return(NA)
  return(round(res,digits=2))
  #return(round(1/(1+(-1 + 1/S)/(lambda)),digits=2))
}

#totalspeedup.bfastts = 1/(1-(c*res$by.total["\"bfastts\"",]$total.pct/100))
#totalspeedup.bfastmonitor= 1/(1-(c*res$by.total["\"bfastmonitor\"",]$total.pct/100))

```

* Speeding up `efp()` by a factor of `r 2` would have sped up `bfastmonitor()` by a factor of `r totalspeedup("efp",2)`
* Speeding up `recresid()` by a factor of `r 2` would have sped up `bfastmonitor()` by a factor of `r totalspeedup("recresid",2)`
* Speeding up `bfastpp()` by a factor of `r 2` would have sped up `bfastmonitor()` by a factor of `r totalspeedup("bfastpp",2)`



## Notes
Given computation times highly depend on the used hardware. In all experiments, a desktop workstation running Ubuntu 14.04 with an Intel Xeon 2.67GHz quad core CPU and 6 GB main memory has been used. Further system information can be found below. To simplify profiling multicore support of R operations was turned off. 


```{r}
suppressPackageStartupMessages(library(bfastSpatial,quietly=T))
sessionInfo()
``` 