---
title: "Profiling Report: bfmSpatial"
output: html_document
---

This report discusses the main results of profiling the bfastmonitor function using randomly generated timeseries.



## Experiment Details

The script to rerun analyses is shown below. 

```{r, eval=F}
library(bfast)
freq = 365
n = 10000

# simple linear trend
mu = 0.5
breakidx = n*0.6
trend1 = (1:n-n/2) / (7*n)
trend2 = 0.12-(1:n-n/2) / (100*n)
trend = c(trend1[1:breakidx],trend2[(breakidx+1):n])
seasonal = 0.1*sin(2*pi*(1:n)/freq)
noise = rnorm(n,0,0.08)
evi.random <- mu + trend + seasonal + noise
series = ts(evi.random,start = c(2001,1), frequency = freq)
plot(series)

bfastmonitor(series, start=c(2015, 1)) 


Rprof(NULL)
Rprof(filename="random_bfastmonitor_1.out",interval=0.01,line.profiling = F)
bfastmonitor(series, start=c(2010, 1), order=3,type="Rec-CUSUM") 
Rprof(NULL)
res = summaryRprof("random_bfastmonitor_1.out")
res$by.total
```




## Results








## Notes
Given computation times highly depend on the used hardware. In all experiments, a desktop workstation running Ubuntu 14.04 with an Intel Xeon 2.67GHz quad core CPU and 6 GB main memory has been used. Further system information can be found below. To simplify profiling multicore support of R operations was turned off. 


```{r}
suppressPackageStartupMessages(library(bfastSpatial,quietly=T))
sessionInfo()
``` 